---
title: "Project5"
author: "Murray Chapman"
date: "03/11/2021"
output: html_document
---

bedroom is at ward - convert to borough
could also probably just use Local Area District Data
Hotel is poly - summarise over borough
Airbnb is points - summarise over borough

```{r library}

library(sf)
library(tidyverse)
library(janitor)
library(here)
library(tmap)

```

```{r wards and boroughs}

LondonBoroughs <- st_read(here::here("statistical-gis-boundaries-london", "ESRI", "London_Borough_Excluding_MHW.shp"))%>%
  clean_names()

LondonWards <- st_read(here::here("statistical-gis-boundaries-london", "ESRI", "London_Ward.shp")) %>%
  clean_names()

```

```{r accomodation data}

OSM <- st_read(here::here("greater-london-latest-free.shp",
                          "gis_osm_pois_a_free_1.shp")) %>%
  st_transform(., 27700)

Airbnb <- read_csv(here::here("listings.csv")) %>%
  st_as_sf(., coords = c("longitude", "latitude"),
           crs = 4326) %>%
  st_transform(., 27700)%>%
  clean_names()

WorldCities <- st_read(here::here("World_Cities",
                          "World_Cities.shp"))

WardBeds <- read_csv(here("bulk.csv"))%>%
  clean_names()

```

```{r beds to borough}

BedsBorough <- LondonWards %>%
  left_join(.,
            WardBeds,
            by = c("gss_code" = "geography_code"))%>%
  group_by(lb_gss_cd)%>%
  summarise(total_beds_per_borough=sum(bedrooms_all_categories_number_of_bedrooms_measures_value, na.rm = TRUE))

```

```{r}

AirbnbBorough <- Airbnb %>% # Number of Airbnbs per borough
  filter(room_type == "Entire home/apt")%>% # We don't want single rooms
  filter(availability_365 == "365")%>% # We want places available yearround
  st_join(LondonBoroughs, .)%>% # Join LondonBoroughs to Airbnb
  group_by(gss_code)%>% # The order to put our data in
  summarise(airbnbcount = n())

```

```{r osm_hotels}

OsmHotels <- OSM %>%
  filter(fclass == "hotel")%>%
  st_join(LondonBoroughs, .)%>%
  group_by(gss_code)%>%
  summarise(hotelcount=n())

```

```{r}

AllDataOne <- LondonBoroughs %>%
  left_join(.,
            BedsBorough,
            by = c("gss_code" = "1b_gss_cd"))

AllDataTwo <- AllDataOne %>%
  left_join(.,
            AirbnbBorough,
            by = c("gss_code" = "gss_code"))

AllDataThree <- AllDataTwo %>%
  left_join(.,
            OsmHotels,
            by = c("gss_code" = "gss_code"))

mapnorm <- all_data_three %>%
  mutate(airbnb_norm=airbnbcount/total_beds_per_borough)%>%
  mutate(hotelnorm=hotelcount/total_beds_per_borough)

```

```{r Extra Info}

WorldCitiesExtract <- WorldCities %>%
  clean_names()%>%
  filter(CNTRY_NAME == "United Kingdom")%>%
  filter(CITY_NAME == "London" | city_name == "Birmingham" | CITY_NAME == "Edinburgh")

UkOutline <- st_read(here::here("gadm36_GBR_shp",
                                "gadm36_GBR_0.shp")) %>%
  
  st_transform(., 27700)

```

```{r mapping}

tmap_mode("plot")

breaks = c(0,5,12,16,57,286)
t <- getJenksBreaks(mapnorm$airbnb_norm, k=5)

tm1 <- tm_shape(mapnorm)+
  tm_polygons("airbnb_norm",
              style="jenks",
              palette="PuBu")+
  tm_legend(show=FALSE)+
  tm_layout("")+
  tm_credits("(a)", position = (0,0.85), size = 1.5)

tm2 <- tm_shape(mapnorm)+
  tm_polygons("hotel_norm",
              style="jenks",
              palette="PuBu")+
  tm_legend(show=FALSE)+
  tm_layout("")+
  tm_credits("(b)", position = (0,0.85), size = 1.5)

newbb <- c(xmin = -29600, ymin=5408, xmax=655696, ymax=1000000)

UK_outlinecrop <- UkOutline$geometry %>%
  st_crop(., newbb)

tm3 <- tm_shape(UkOutline)+
  tm_polygons(col="darkslategray1")+
  tm_layout(frame=FALSE)+
  tm_shape(WorldCitiesExtract)+
  tm_symbols(col="red", scale=.5)+
  tm_text("city_name", xmod=-1, ymod=-0.5)

legend <- tm_shape(mapnorm)+
  tm_polygons("hotelnorm",
              style="jenks",
              palette="PuBu")+
  tm_scale_bar(position=c(0.2,0.04), text.size=0.6)+
  tm_compass(north=0, position=c(0.65,0.6))+
  tm_layout(legend.only = TRUE, legend.position=c(0.2,0.25), asp=0.1)+
  tm_credits("(c) OpenStreetMap contrbutors and Air b n b", position=c(0.0,0.0))

t=tmap_arrange(tm1, tm2, tm3, legend, ncol=2)

```

```{r insetmap}

tmmain <- tm_shape(mapnorm)+
  tm_polygons("airbnb_norm",
              style="jenks",
              palette="PuBu")+
  tm_scale_bar(position = c("left", "bottom"), text.size = .75)+
  tm_layout(frame=FALSE)+
  tm_credits("(c) OpenStreetMap contributors and Air b n b", position=c(0.0,0.0))+
  tm_compass(type = "8star", position =c(0.06, 0.1))

LondonBB <- st_bbox(mapnorm)%>%
  st_as_sfc() # Make into a spatial feature

inset <- tm_shape(Uk_coutlinecrop)%>%
  tm_polygons(col="grey40", lwd=1)+ #Plot the polygon with this line width
  tm_shape(LondonBB)+
  tm_layout(frame=FALSE, bg.color="transparent")+ 
  tm_shape(WorldCitiesExtract)+
  tm_symbols(col = "red", scale = .5)+
  tm_text("city_name", xmod=-1.5, ymod=-0.5)%>%
  

print(inset, vp = viewport(0.86, 0.29, width = 0.5, height = 0.55))